Highlighting Disputed Information on the Web

### 2009-10-25 papers/www_disputefinder/disputefinder.tex
Improved system description

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion.png}
	\caption{Popup interface with articles for and against a claim}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a "don't mark this" button}

@@

\item[How do we highlight snippets?] How do we tell what web page a user is reading, and augment their interface to alert them about disputed claims? Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension~\cite{nolike-extension?}. Using a proxy~\cite{proxy?} has similar adoption problems to a browser extension, and is likely to break some web sites. If external sites such as news readers and search engines use our API then they can provide information about disputed claims to users without them having to install anything, but this limits coverage to content accessed through sites that use the API.

@@

LLM is far from being state of the art and many more sophisticated algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}.

While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown. Naturally, as processor speeds improve, it will become practical to use increasingly sophisticated algorithms.

@@

\subsection{Finding Disputed Information on the Web}

An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.

Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic. Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.

\subsection{Extracting Information from the Web}

Information extration tools such as TextRunner~\cite{Etzioni2008} 
Read The Web

TextRunner~\cite{Etzioni2008}

\todo{cite lots of Etzioni stuff}

\cite{SnowBall}
\cite{Read The Web}
\cite{Information Extraction from Wikipedia}
\cite{KnowItAll}
\cite{TextRunner}

\todo{Online Dispute Resolution}

\todo{Cite Kittur et al}

@@

\subsection{Persuasive Technology}

@@

Users interact with Dispute Finder in two ways. Skeptical readers browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims. Activists tell Dispute Finder about disputed claims that they care about, and add evidence to support their point of view.

@@

Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust. We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.

Dispute Finder uses two mechanisms to inform a user when information on the page they are reading is disputed. It highlights any snippets that make the disputed claims in red, and it displays a message bar.

The message bar alerts the user that they should look out for highlighted snippets on the current page. 
Highlighted snippets can be difficult to see if the page is using a background color that is similar to our highlight color\footnote{We tried to choose a color that is rarely used as a background} or if the user is color blind. The message also provides a ``go to next snippet'' button that allows the user to step though the highlighted snippets one at a time.

The highlights show a user {\it why} Dispute Finder thinks that a page is making a disputed claim. In some cases Dispute Finder may have mistakenly thought an article was saying something it wasn't, or the disputed claim may be in text the user isn't interested in, such as a comment. If Dispute Finder has incorrectly marked a snippet as making a disputed claim then the user is encouraged to tell Dispute Finder this by clicking on the snippet and then cliking on the ``report incorrect highlighing'' button in the popup interface.

A user can discover what disputed claim Dispute Finder thinks a snippet is making by hovering their mouse over it, and can bring up more information about a claim by clicking on the snippet (Figure\ref{claimview}).

There is little point repeatedly telling a user that the same claim is disputed. In our current version, a user can ask Dispute Finder to not highlight a claim again by clicking on the ``ignore this claim]'' button in the popup interface. An alternative is to automatically stop highlighting a disputed claim, once the user has brought up the popup interface for it once. We have not yet conclusively decided which method works better. Requiring a user to manually opt out of a claim requires more work from the user, but also causes less user-confusion as users do not normally expect viewing something to be a destructive operation.

A web site can also opt to use the Dispute Finder API to detect disputed claims on the content that they present to users. This API could be particularly useful to tools like search engines and RSS feed readers that a user may use to access a large proportion of the information they consume. The firefox extension itself uses the same API. The advantage of using the Firefox extension is that it can look for disputed claims on any web site. The disadvantage is that it can only be used by users who use a compatible browser and are prepared to install an extension (well known to be a significant barrier to adoption\cite{extension-bad?}

@@

Once a user has been informed that the page they are reading is making a disputed claim, they will typically be interested in learning more about that claim, so they can judge whether there are alternative points of view that they should take seriously.

The simplest option would be to merely inform the user that the page is making a disputed claim, but provide no further information about that claim.The user could then use a tool such as a search engine to investigate the claim further.

There are several reasons why it is useful to associate a claim with information justifying alternative points of view:

\begin{itemize}
\item To allow a user to quickly determine whether alternative points of view are sufficiently credible that they should take them seriously
\item To allow users who are moderating the database to determine when no arguments exist for other points of view, and thus the claim should not be in the database
\item To allow Dispute Finder's algorithms to determine whether the claim is disputed by someone that that particular user would take seriously. Although we have not yet implemented such features, we believe they will be important.
\end{itemize}

@@

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them an IBIS-style\cite{gibis} argumentation graph that explains the structure of the argument against the claim. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of sources that argue in favor of that claim (Figure\ref{arg-graph?})

\item[Source lists:] Dispute Finder shows the user two lists of sources, one of which contains sources arguing in favor of the claim, and the other of which contains sources arguing against the claim (Figure~\ref{article-list})
\end{description}

The argumentation graph is potentially much more powerful. When a user is presented with a simple list of sources, several of them may be making the same core points and it may not be obvious that one of the sources is making a point that the user had not come across before. The argumentation graph also allows the user to browse around the network of different claims being made about an area, which can be interesting in itself.

On important disadvantage of using an argumentation graph is that someone has to build it. In our prototype, the argumentation graph was built entirely by users. We found that our users had difficulty creating well structured argumentation graphs that were useful for other users, a result that is consistent with previous studies~\cite{ibis-bad?}. It is possible that an alternative (simpler?) graph structure or interface that made it easier to build such graphs might make them work better. Argumentation graphs might also work better if they could be built automatically by mining the web.

Another point in favor of using a simple list of sources is that we found that users are far more concerned with ``who'' disputes a claim, than what their argument is. For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with. The argumentation graph focusses on presenting the user with the structure of the argument against the claim, but our studies suggest that the user is likely to find this much less interesting than the authority behind the arguments against the claim.

In the present version of Dispute Finder, a source can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable. Good sources include newspapers, universities, respected organizations, and Wikipedia itself. Users can vote on whether they think a particular source is useful, and this voting determines the order in which sources are listed. A user can also request that a source be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable sources. Users with moderator privileges review requests for deletion and delete claims and sources that do not meet requirements.

\todo{study result: verify}
There are significant weaknesses in this approach. In our studies, we found that users disagree about what they would consider a reliable source. Users consider a source to be reliable if it espouses opinions that they themselves agree with, and is accepted as being a reliable source within their social group. There may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who want to hide good arguments against a claim that they support by voting up bad ones. Another problem is that, by resorting to moderators to decide which sources and claims are high enough quality to be included, we open ourselves up to charges of bias.

In the future it may be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.

There is a difficult trade-off here. If we only show users sources that we believe they are likely to trust, then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against. On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment, and stifling the voices of those who are less widely respected by the establishment, but may be right. If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously. We do not yet claim to know a good solution for this problem.

@@

\section{Studying the Users}

@@

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where the facts can change fast. If Dispute Finder is to be effective for describing such events then it will need to have better support associating times with claims and snippets.

@@

The biggest problem that Dispute Finder has right now is that its coverage is not very high. Both our database of disputed claims, and the number of snippets that we highlight that make each disputed claim

In its current state, it is unlikely that a user will see a snippet highlighted that makes a claim that they did

>>>>

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Popup interface with articles for and against a claim}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a "don't mark this" button}

@@

\item[How do we highlight snippets?] How do we tell what web page a user is reading, and augment their interface to alert them about disputed claims? Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension. Using a proxy~\cite{Barrett1997} has similar adoption problems to a browser extension, and is likely to break some web sites. If external sites such as news readers and search engines use our API then they can provide information about disputed claims to users without them having to install anything, but this limits coverage to content accessed through sites that use the API.

@@

LLM is far from being state of the art and many more sophisticated algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter2008} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

While Dispute Finder would almost certainly improve its precision and recall if it used a more sophisticated algorithm, LLM has the advantage of being simple enough to run efficiently inside a user's web browser for every page they look at without causing a noticeable slowdown. We do however believe that there is scope to use more sophisticated algorithms, particularly as processor speeds improve.

@@

%
%\subsection{Finding Disputed Information on the Web}
%
%An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
%
%Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic. Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.
%
%\subsection{Extracting Information from the Web}
%
%Information extration tools such as TextRunner~\cite{Etzioni2008} 
%Read The Web
%
%TextRunner~\cite{Etzioni2008} 
%
%\todo{cite lots of Etzioni stuff}
%
%\cite{SnowBall}
%\cite{Read The Web}
%\cite{Information Extraction from Wikipedia}
%\cite{KnowItAll}
%\cite{TextRunner}
%
%\todo{Online Dispute Resolution}
%
%\todo{Cite Kittur et al}

@@

%\subsection{Persuasive Technology}

@@

Users interact with Dispute Finder in two ways. {\it Skeptical Readers} browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims. {\it Activists} tell Dispute Finder about disputed claims that they care about, add evidence to support their point of view, and help teach Dispute Finder to recognize particular claims on the web.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_bar.png}
	\caption{Highlight and Notification Bar}
	\label{highlight_bar}
	\end{center}
\end{figure}

%Dispute Finder is designed to alert a user when information they read on a web page makes a claim that is disputed by a source they might trust. 
%
%
%Dispute Finder aims to inform users when information they read on the web makes claims that are disputed by sources that they might trust. We are particularly interested in informing users about claims that they hadn't thought about before, hadn't realized were disputed by sources they repect, or have not yet established a strong opinion on.

The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed. It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).

The notification bar alerts the user that they should look out for highlighted snippets. Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors} or if the user is color blind. The notification bar also allows a user to step through the highlighted snippets on the page.

The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims. This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the "report incorrect highlighting" button from the popup interface.

Once a user is aware that a claim is disputed, there is little point telling them about the same disputed claim again in the future. We have not yet concluded whether it is better for Dispute Finder to automatically stop highlighting a claim once a user has viewed the claim, or whether it is better for a user to explicitly ask Dispute Finder to stop highlighting a claim. In our current implementation, a user can tell Dispute Finder to not highlight a claim again by setting the ``don't highlight this claim for me again'' checkbox in the popup interface (Figure~\ref{claimview}). Requiring a user to manually opt out of a claim requires more work from the user, but hiding already viewed claims can be confusing, since users do not normally expect viewing something to be a destructive operation. A compromise position is to highlight claims that have been seen before in a fainter color; similar to the way links are typically colored on web pages.

\todo{Try using a fainter color}

\todo{Text is wrong in the screenshot}

Dispute Finder also provides an API that can be used by other sites to determine whether their content makes disputed claims. For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.

@@

If a user clicks on a highlighted snippet, Dispute Finder will bring up a popup interface explaining the different alternative points of view. We could have ommitted this feature and still had a useful system. Once a user sees that something is disputed, they could use an alternative service, such as a search engine, Wikipedia, Politifact or Snopes, to find further information about the claim. There are however several reasons why it makes sense for Dispute Finder to maintain information about a disputed claim:

\begin{description}
\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying. By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
\end{description}

Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.

@@

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph~\cite{Conklin1987a}. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{claimview}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting "use as evidence" from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

The argumentation graph makes it easier to see {\it why} a claim is disputed, while the article lists make it easier to see {\it who} supports or opposes the claim.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_evidence.png}
	\caption{Adding an article, with a summary sentence selected}
	\label{add_article}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
	\caption{Choose how to connect an article with a claim}
	\label{article_choose}
	\end{center}
\end{figure}

\todo{Call them supporting pages? Naming is a mess right now.}

When using the article list approach, several different articles may be expressing essentially the same point of view and it may not be obvious that one of the articles is making a point that the user had not come across before. The argumentation graph allows the user to easily see what the range of different opinions is, and quickly see if there is an argument that they have not encountered before.

A significant weakness of the argumentation graph approach is that a good argumentation graph takes significantly more effort to build than a simple list of articles. In our prototype the argumentation graph was built entirely by users and we found that our users had difficulty creating graphs that were useful for other users. There were two problems here: firstly, breaking down all the different arguments for and against a claim takes much more time than just adding articles to a list, particularly given that a single article will often make several different opposing points; secondly, we found that users had difficulty creating well structured argumentation graphs, as we outline in Section~\ref{user-studies}. This result is consistent with previous studies~\cite{Isenmann1997}.

Another point in favor of using a simple list of sources is that most of the users we talked to seemed to be more interested in {\it who} disputed a claim, rather than what their argument was. For example, if a user is a reader of the New York Times, and they hear that the New York Times argues against the claim they are reading, then they will take the dispute much more seriously than if the key article arguing against the claim is from a source they are not familiar with. Moreover, we found that when a user wanted to understand {\it why} a claim is disputed, they prefered to read whichever article seemed to be most credible, rather than browsing an argumentation graph.

It is possible that the best solution would be a visualisation that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.

\subsection{Trustworthy Sources}

In the current version of Dispute Finder, an article can be any web page that meets the Wikipedia criteria\footnote{http://en.wikipedia.org/wiki/Wikipedia:SOURCES} for being reliable. Good sources of articles include newspapers, universities, respected organizations, and Wikipedia itself. Users can vote on whether they think a particular article is useful, and this voting determines the order in which articles are listed. A user can also request that an article be deleted if it is not relevant to the claim, or request that a claim be deleted if it is not disputed by any reliable articles. Users with moderator privileges review requests for deletion and delete claims and articles that do not meet requirements.

\todo{study result: verify}
There are significant weaknesses in this approach. Pew have shown~\cite{pew-news} that different people trust different sources. There may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

It may thus be better to learn what sources a particular user is likely to believe are reliable, and then adjust both what sources Dispute Finder shows to the user, and what claims are highlighted, based on this.

There is a difficult trade-off here. If we only show users sources that we believe they are likely to trust and only highlight claims as disputed if they are disputed by sources that share the user's own worldview then we risk reinforcing the echo-chamber effect that Dispute Finder is intended to fight against. On the other hand, if we only provide information from sources that are widely regarded as being reliable, we risk enforcing the beliefs of the establishment and stifling the voices of those who are less accepted by the establishment, but may still be right. If we pay no attention to what sources the user trusts, or what sources are regarded as respectable, then we may waste time trying to persuade users using sources that they would not take seriously. We do not yet claim to know a good solution for this problem, but we believe it is an interesting area for further research.

@@

\section{Learning from Users}

@@

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked one claim as opposing another claim when they were referring to similar incidents that occurred at different times.

When using the article-list interface, several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative. For example a user would mark an article that opposed global warming as opposing the claim "global warming is bad" because the article opposed global warming.

@@
